Monte Carlo and bootstrap for ALL parameters

### 2024-08-14 All_param.Rmd
Coverage rates rectified

  # Estimations of totals
  for (c in 1:nboot) {
    big_est <- mapply(function(vec_, j){
        vec_[c] <- (n/(n-1))*sum(df[, 2 + j + ((nb_var+2)*(c-1))]/p)
        return(as.data.frame(vec_))
        }, big_est, 1:nb_var)
    # (n/(n-1)) is the correction needed since we choose only (n-1) points
  }
  # Estimations of ratios
  l_big_est <- length(big_est)
  big_est <- as.data.frame(big_est)
  for (k in 1:4) {
    big_est <- add_column(big_est, rep(NA, nrow(big_est)))
  }
  for (c in 1:nboot) {
    ratio_c <- mapply(function(j){big_est[c,j+4]/big_est[c,j]
    }, 1:4) # 4 ratios
    big_est[c, (l_big_est+1):(l_big_est+4) ] <- ratio_c
  }
  colnames(big_est) <- paste0("est_", raw_names)[-(1:2)]
  return(big_est)
  # Data frame with 3 estimations for each sample
}
```

@@

    # Confidence intervals
    norm_CI <- data.frame(matrix(numeric(0), nrow = 2))
    perc_CI <- data.frame(matrix(numeric(0), nrow = 2))
    rev_perc_CI <- data.frame(matrix(numeric(0), nrow = 2))
    # norm_CI <- data.frame(useless = rep(0, 2))
    # perc_CI <- data.frame(useless = rep(0, 2))
    # rev_perc_CI <- data.frame(useless = rep(0, 2))
    for (l in 1:length(est_boot_val)) { # Loop: one estimator each time
      sorted_est <- sort(est_boot_val[,l])
      lim_inf <- sorted_est[floor(B2*2.5/100)]
      lim_sup <- sorted_est[B2 - floor(B2*2.5/100)]
      perc_CI <- cbind(perc_CI, data.frame(c(lim_inf, lim_sup)))
      rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(as.numeric(est_b[l])*2 - lim_sup, as.numeric(est_b[l])*2 - lim_inf)))
      norm_CI <- cbind(norm_CI, data.frame(c(as.numeric(est_b[l])-qnorm(0.975)*sqrt(var(est_boot_val[,l])), as.numeric(est_b[l])+qnorm(0.975)*sqrt(var(est_boot_val[,l])))))
    }
    # norm_CI$useless <- NULL
    # perc_CI$useless <- NULL
    # rev_perc_CI$useless <- NULL
    nam_lim <- paste0("lim_", raw_names)[-(1:2)]
    colnames(norm_CI) <- nam_lim
    colnames(perc_CI) <- nam_lim
    colnames(rev_perc_CI) <- nam_lim
    BCa_CI <- bcanon(df_b, est_b, est_boot_val, p, nb_var)
    colnames(BCa_CI) <- nam_lim
    all_CI <- list(Normal = as.data.frame(norm_CI), Percentile = as.data.frame(perc_CI), `Reverse percentile` = as.data.frame(rev_perc_CI), BCa = as.data.frame(BCa_CI))
    BOOT_CI[[b]] <- all_CI
    names(BOOT_CI)[b] <- paste0("CI", b)
  }
  return(list(`Local Variables` = BOOT_df, Estimations = BOOT_est, Variances = BOOT_var, `Confidence Intervals` = BOOT_CI))
  # Local Variables: local variables (number and volume) for each point in each sample
  # Estimations: 3 estimations (number, volume, ratio volume / number) for each sample
  # Variances: mean of the bootstrap variance for each estimator
  # Confidence Intervals: 3 different forms of 95% confidence intervals, for each total / ratio
}
```

@@

res2 <- MC_boot(n, B1 = 1000, B2 = 400)
# Just one circle to begin with

@@

```{r}
# We want all the variances obtained for each parameter of interest, 
# to find the mean for each of these series
raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
EST_names <- paste0("EST_", raw_names)[-(1:2)]
# est_names <- paste0("est_", raw_names)[-(1:2)]

@@

  raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
  CI_names <- paste0("CI_", raw_names)[-(1:2)]
  TC_names <- paste0("TC_", raw_names)[-(1:2)]
  low_names <- paste0("low_", raw_names)[-(1:2)]
  up_names <- paste0("up_", raw_names)[-(1:2)]
  length_names <- paste0("length_", raw_names)[-(1:2)]

@@

  for (j in CI_names) {
    assign(j, data.frame(matrix(numeric(0), nrow = 2)))
  }
  # CI_nb <- data.frame(matrix(numeric(0), nrow = 2))
  # CI_vol <- data.frame(matrix(numeric(0), nrow = 2))
  # CI_ratio <- data.frame(matrix(numeric(0), nrow = 2))
  for (elt in res2$`Confidence Intervals`) { # For each MC iteration
    for (j in CI_names) { # For each estimation
      x <- cbind(get(x = j), elt[k])
      assign(j, x)
    }
    # elt2 <- as.data.frame(elt[k])
    # CI_nb <- cbind(CI_nb, elt2[k])
      # cbind(CI_nb2, c(elt2[k][1,], elt2[k][2,]))

@@

```{r}
diff_percent <- function(x,y){100*(max(res1$Variances[x],mean(unlist(y)))-min(res1$Variances[x],mean(unlist(y))))/min(res1$Variances[x],mean(unlist(y)))}
cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(1, VAR_nb), "%", "\n - for the volume of trees: ", diff_percent(5, VAR_vol), "%\n - for the ratio volume / number of trees: ", diff_percent(9, VAR_ratio), "%", 
    "\n\n - for the number of small trees:", diff_percent(2, VAR_nb_s), "%", "\n - for the volume of small trees:", diff_percent(6, VAR_vol_s), "%", "\n - for the ratio volume / number of trees:", diff_percent(10, VAR_ratio_s), "%",
    "\n\n - for the number of medium trees:", diff_percent(3, VAR_nb_m), "%", "\n - for the volume of medium trees:", diff_percent(7, VAR_vol_m), "%", "\n - for the ratio volume / number of trees:", diff_percent(11, VAR_ratio_m), "%",
    "\n\n - for the number of big trees:", diff_percent(4, VAR_nb_b), "%", "\n - for the volume of big trees:", diff_percent(8, VAR_vol_b), "%", "\n - for the ratio volume / number of trees:", diff_percent(12, VAR_ratio_b), "%",
    sep = "")

>>>>

  # Estimations of totals
  for (c in 1:nboot) {
    big_est <- mapply(function(vec_, j){
        vec_[c] <- (n/(n-1))*sum(df[, 2 + j + ((nb_var+2)*(c-1))]/p)
        return(as.data.frame(vec_))
        }, big_est, 1:nb_var)
    # (n/(n-1)) is the correction needed since we choose only (n-1) points
  }
  # Estimations of ratios
  l_big_est <- length(big_est)
  big_est <- as.data.frame(big_est)
  for (k in 1:4) {
    big_est <- add_column(big_est, rep(NA, nrow(big_est)))
  }
  for (c in 1:nboot) {
    ratio_c <- mapply(function(j){big_est[c,j+4]/big_est[c,j]
    }, 1:4) # 4 ratios
    big_est[c, (l_big_est+1):(l_big_est+4) ] <- ratio_c
  }
  colnames(big_est) <- paste0("est_", raw_names)[-(1:2)]
  return(big_est)
  # Data frame with estimations for each sample
}
```

@@

    # Confidence intervals
    norm_CI <- data.frame(matrix(numeric(0), nrow = 2))
    perc_CI <- data.frame(matrix(numeric(0), nrow = 2))
    rev_perc_CI <- data.frame(matrix(numeric(0), nrow = 2))
    # norm_CI <- data.frame(useless = rep(0, 2))
    # perc_CI <- data.frame(useless = rep(0, 2))
    # rev_perc_CI <- data.frame(useless = rep(0, 2))
    for (l in 1:length(est_boot_val)) { # Loop: one estimator each time
      sorted_est <- sort(est_boot_val[,l])
      lim_inf <- sorted_est[floor(B2*2.5/100)]
      lim_sup <- sorted_est[B2 - floor(B2*2.5/100)]
      perc_CI <- cbind(perc_CI, data.frame(c(lim_inf, lim_sup)))
      rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(as.numeric(est_b[l])*2 - lim_sup, as.numeric(est_b[l])*2 - lim_inf)))
      norm_CI <- cbind(norm_CI, data.frame(c(as.numeric(est_b[l])-qnorm(0.975)*sqrt(var(est_boot_val[,l])), as.numeric(est_b[l])+qnorm(0.975)*sqrt(var(est_boot_val[,l])))))
    }
    # norm_CI$useless <- NULL
    # perc_CI$useless <- NULL
    # rev_perc_CI$useless <- NULL
    nam_lim <- paste0("lim_", raw_names)[-(1:2)]
    colnames(norm_CI) <- nam_lim
    colnames(perc_CI) <- nam_lim
    colnames(rev_perc_CI) <- nam_lim
    BCa_CI <- bcanon(df_b, est_b, est_boot_val, p, nb_var)
    colnames(BCa_CI) <- nam_lim
    all_CI <- list(Normal = as.data.frame(norm_CI), Percentile = as.data.frame(perc_CI), `Reverse percentile` = as.data.frame(rev_perc_CI), BCa = as.data.frame(BCa_CI))
    BOOT_CI[[b]] <- all_CI
    names(BOOT_CI)[b] <- paste0("CI", b)
  }
  return(list(`Local Variables` = BOOT_df, Estimations = BOOT_est, Variances = BOOT_var, `Confidence Intervals` = BOOT_CI))
  # Local Variables: local variables (number and volume) for each point in each sample
  # Estimations: estimations (numbers, volumes, ratios volume / number) for each sample
  # Variances: mean of the bootstrap variance for each estimator
  # Confidence Intervals: 4 different forms of 95% confidence intervals, for each total / ratio
}
```

@@

res2 <- MC_boot(n, B1 = 200, B2 = 100)
# Just one circle to begin with

@@

```{r}
# We want all the variances obtained for each parameter of interest, 
# to find the mean for each of these series
raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
EST_names <- paste0("EST_", raw_names)[-(1:2)]

@@

  raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
  nam_lim <- paste0("lim_", raw_names)[-(1:2)]
  CI_names <- paste0("CI_", raw_names)[-(1:2)]
  TC_names <- paste0("TC_", raw_names)[-(1:2)]
  low_names <- paste0("low_", raw_names)[-(1:2)]
  up_names <- paste0("up_", raw_names)[-(1:2)]
  length_names <- paste0("length_", raw_names)[-(1:2)]

@@

  for (j in CI_names) {
    assign(j, data.frame(matrix(numeric(0), nrow = 2)))
  }
  # CI_nb <- data.frame(matrix(numeric(0), nrow = 2))
  # CI_vol <- data.frame(matrix(numeric(0), nrow = 2))
  # CI_ratio <- data.frame(matrix(numeric(0), nrow = 2))
  for (elt in res2$`Confidence Intervals`) { # For each MC iteration
    for (j in 1:length(CI_names)) { # For each estimation
      x <- cbind(get(x = CI_names[j]), elt[k][[1]][colnames(elt[k][[1]]) == nam_lim[j]]) # elt[k]
      assign(CI_names[j], x)
    }
    # elt2 <- as.data.frame(elt[k])
    # CI_nb <- cbind(CI_nb, elt2[k])
      # cbind(CI_nb2, c(elt2[k][1,], elt2[k][2,]))

@@

```{r}
diff_percent <- function(x,y){100*(max(res1$Variances[x],mean(unlist(y)))-min(res1$Variances[x],mean(unlist(y))))/min(res1$Variances[x],mean(unlist(y)))}
cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(1, VAR_nb), "%", "\n - for the volume of trees: ", diff_percent(5, VAR_vol), "%\n - for the ratio volume / number of trees: ", diff_percent(9, VAR_ratio), "%", 
    "\n\n - for the number of small trees: ", diff_percent(2, VAR_nb_s), "%", "\n - for the volume of small trees: ", diff_percent(6, VAR_vol_s), "%", "\n - for the ratio volume / number of trees: ", diff_percent(10, VAR_ratio_s), "%",
    "\n\n - for the number of medium trees: ", diff_percent(3, VAR_nb_m), "%", "\n - for the volume of medium trees: ", diff_percent(7, VAR_vol_m), "%", "\n - for the ratio volume / number of trees: ", diff_percent(11, VAR_ratio_m), "%",
    "\n\n - for the number of big trees: ", diff_percent(4, VAR_nb_b), "%", "\n - for the volume of big trees: ", diff_percent(8, VAR_vol_b), "%", "\n - for the ratio volume / number of trees: ", diff_percent(12, VAR_ratio_b), "%",
    sep = "")
